Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-20 tex/paper1/paper1.tex
another first draft

\keywords{???}

@@

The ratio of the two components $G(\nu)/P_{1}(\nu)$ measures the
relative contribution of the ``excess'' emission over the
\PL\ component.  The frequency $\nu_{max}$ is the frequency at which
this ratio is a maximum, and indicates the most likely frequency at
which the signal of the $G(\nu)$ contribution is strongest.  The
ratios maximize in the range $2.18 \le \nu_{max} \le 4.63$ mHz.  This
is in the frequency range suggested by the moss observations of
\cite{2003ApJ...595L..63D}.  If Model 2 is indeed a reasonable model
of the \Fpa\ in the regions studied, then the $G(\nu)$ contribution is
consistent with previous observations.

@@

We are grateful to the developers of SSWIDL
\citep{1998SoPh..182..497F}, IPython \citep{ipython}, SunPy
\citep{mumford-proc-scipy-2013}, PyMC
\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}, matplotlib
\citep{Hunter:2007} and Scientific Python stack for providing data
preparation, manipulation, analysis and display packages.  This work
was supported by NASA award NNX13AE03G S01 funded through NASA ROSES
NNH12ZDA001N-SHP.

@@

\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt{2\pi\sigma^{2}}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$,
$N_{f}$ is the number of Fourier frequencies, and $\sigma_{j}$ is the
normal distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution, and are given
in Table \ref{tab:priors}.  Each MCMC chain that was run took 100,000
samples, with burn-in assumed to be at 50,000 samples.  The chain is
thinned by taking every fifth element in the chain, forming the final
sample from which the parameter estimates and their uncertainties are
calculated.
\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{parameter} &
\colhead{Model 1} &
\colhead{Model 2} \\
}
\startdata
$A$ & $4.5 \times 10^{-5} \rightarrow 22026$ &  $4.5 \times 10^{-5} \rightarrow 22026$\\
$n$  &  $-1\rightarrow 6$   & $-1\rightarrow 6$  \\
$C$ & $2.1 \times 10^{-9} \rightarrow 22026$  & $2.1 \times 10^{-9} \rightarrow 22026$  \\
$\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
$\beta$ & not applicable  & $0.5 - 10$\tablenotemark{1} (mHz)\\
$\delta$ & not applicable & $0.001\rightarrow 3$ (decades of frequency)\\
\enddata
\tablenotetext{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal
distribution to lie within the prior range.}
\end{deluxetable}
The \mFpa\ are assumed to
be normally distributed with a width given by $\sigma_{mean}$ as
calculated above.  A five step fitting process is used to fit Models 1
and 2 to the data, and is described below.

>>>>

\keywords{Sun: corona, Sun: oscillations, methods: data analysis,
  methods: statistical}

@@

The ratio of the two components $G(\nu)/P_{1}(\nu)$ measures the
relative contribution of the ``excess'' emission over the
\PL\ component.  The frequency $\nu_{max}$ is the frequency at which
this ratio is a maximum, and indicates the most likely frequency at
which the signal of the $G(\nu)$ contribution is strongest.  The
ratios maximize in the range $1.34 \le \nu_{max} \le 4.72$ mHz.  This
is in the frequency range suggested by the moss observations of
\cite{2003ApJ...595L..63D}.  If Model 2 is indeed a reasonable model
of the \Fpa\ in the regions studied, then the $G(\nu)$ contribution is
consistent with previous observations.

@@

We are grateful to the developers of SSWIDL
\citep{1998SoPh..182..497F}, IPython \citep{ipython}, SunPy
\citep{mumford-proc-scipy-2013}, PyMC
\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}, matplotlib
\citep{Hunter:2007} and the Scientific Python stack for providing data
preparation, manipulation, analysis and display packages.  This work
was supported by NASA award NNX13AE03G S01 funded through NASA ROSES
NNH12ZDA001N-SHP.

@@

\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt{2\pi\sigma^{2}}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$,
$N_{f}$ is the number of Fourier frequencies, and $\sigma_{j}$ is the
normal distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution, and are given
in Table \ref{tab:priors}.  Each MCMC chain that was run took 100,000
samples, with burn-in assumed to be at 50,000 samples.  The chain is
thinned by taking every fifth element in the chain, forming the final
sample from which the parameter estimates and their uncertainties are
calculated.
\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{parameter} &
\colhead{Model 1} &
\colhead{Model 2} \\
}
\startdata
$A$ & $4.5 \times 10^{-5} \rightarrow 22026$ &  $4.5 \times 10^{-5} \rightarrow 22026$\\
$n$  &  $-1\rightarrow 6$   & $-1\rightarrow 6$  \\
$C$ & $2.1 \times 10^{-9} \rightarrow 22026$  & $2.1 \times 10^{-9} \rightarrow 22026$  \\
$\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
$\beta$ & not applicable  & $0.5 - 10$ (mHz)\tablenotemark{1}\\
$\delta$ & not applicable & $0.001\rightarrow 3$ (decades of frequency)\\
\enddata
\tablenotetext{1}{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal
distribution to lie within the prior range.}
\end{deluxetable}
The \mFpa\ are assumed to
be normally distributed with a width given by $\sigma_{mean}$ as
calculated above.  A five step fitting process is used to fit Models 1
and 2 to the data, and is described below.
